---
title: "Practical machine learning Project"
author: "morgan"
date: "12/5/2020"
output: html_document
---
## Title : Practical machine learning week4 assignment
##The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. You may use any of the other variables to predict with. You should create a report describing how you built your model, how you used cross validation, what you think the expected out of sample error is, and why you made the choices you did. You will also use your prediction model to predict 20 different test cases.
--------
##Loading and preprocessing the data
##1.Load the data
```{r echo=TRUE}
traindata <- read.csv("/Users/lydc/datascience/practical machine learning/pml-training.csv",na.strings=c("NA","#DIV/0!", ""))
testdata <- read.csv("/Users/lydc/datascience/practical machine learning/pml-testing.csv",na.strings=c("NA","#DIV/0!", ""))
```
##2.Preprocess the data
```{r echo=TRUE}
NA_num <-sapply(traindata, function(y) sum(length(which(is.na(y)))))
NA_num <- data.frame(NA_num)
NA_num$name<-rownames(NA_num)
NA_num
testdata <- testdata[ , colSums(is.na(traindata)) == 0 ]
traindata <- traindata[ , colSums(is.na(traindata)) == 0]
#remove irrelevant columns
testdata <- testdata[,-c(1:7)]

traindata <- traindata[,-c(1:7)]
```
##3.Cross Validation
```{r echo=TRUE}
library(caret)
data_part <- createDataPartition(y=traindata$classe, p=0.75, list=FALSE)
train1 <- traindata[data_part, ] 
test1 <- traindata[-data_part, ]
```

##4.classfication Tree
```{r echo=TRUE}
library(rpart)
library(rpart.plot)
model <- rpart(classe ~ ., data=train1, method="class")
prediction <- predict(model, test1, type = "class")
confusionMatrix(prediction, test1$classe)
#Accruacy = 74.41%
rpart.plot(model)
```
##5.Random forest
```{r echo=TRUE}
library(randomForest)
model2 <- randomForest(classe ~. , data=train1, method="class")
prediction2 <- predict(model2, test1, type = "class")
confusionMatrix(prediction2, test1$classe)
#Accuracy > 99.5%, Random forest is better
```
##Final Model and Prediction
```{r}
predictionfinal <- predict(model2, testdata , type="class")
predictionfinal
```
