---
title: "Practical machine learning Project"
author: "morgan"
date: "8/5/2020"
output: html_document
---
## Title : Practical machine learning week4 assignment
##The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. You may use any of the other variables to predict with. You should create a report describing how you built your model, how you used cross validation, what you think the expected out of sample error is, and why you made the choices you did. You will also use your prediction model to predict 20 different test cases.
--------
##Loading and preprocessing the data
##1.Load the data
```{r echo=TRUE}
library(caret)
traindata <- read.csv("/Users/lydc/datascience/practical machine learning/pml-training.csv",row.names = 1)
testdata <- read.csv("/Users/lydc/datascience/practical machine learning/pml-testing.csv",row.names = 1)
```
##2.Reduce the number of features by removing variables with nearly zero variance and variables that are almost always NA on traindata
```{r echo=TRUE}
nsv <- nearZeroVar(traindata, saveMetrics = T)
traindata <- traindata[, !nsv$nzv]
nav <- sapply(colnames(traindata), function(x) if(sum(is.na(traindata[, x])) > 0.8*nrow(traindata)){return(T)}else{return(F)})
traindata <- traindata[, !nav]
#Calculate correlation
cor <- abs(sapply(colnames(traindata[, -ncol(traindata)]), function(x) cor(as.numeric(traindata[, x]), as.numeric(traindata$classe), method = "spearman")))
```
##Model Building
##1.Boosting model
```{r echo=TRUE}
#Fit model with boosting algorithm and 10-fold cross validation to predict `classe` with all other predictors.  
set.seed(1234)
boostFit <- train(classe ~ ., method = "gbm", data = traindata, verbose = F, trControl = trainControl(method = "cv", number = 10))
boostFit
plot(boostFit, ylim = c(0.9, 1))
#The boosting algorithm generated a good model with accuracy = 0.997
```
##2.Random forests model
```{r echo=TRUE}
library(randomForest)
set.seed(123)
rfFit <- train(classe ~ ., method = "rf", data = traindata, importance = T, trControl = trainControl(method = "cv", number = 10))
rfFit
plot(rfFit, ylim = c(0.9, 1))
#The random forests algorithm generated a very accurate model with accuracy close to 1.
#Compared to boosting model, this model generally has better performance in terms of accuracy.
```
##Final Model and Prediction
```{r}
rfFit$finalModel
prediction <- as.character(predict(rfFit, testing))
```
